Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-02 MultipleRoundSims/sections/05-results1.tex
deleted risk graph

\begin{figure}
\begin{centering}
\includegraphics[width=0.8\textwidth]{minerva25percthen1p5_sprob.png}
\caption{This plot shows, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$, round size multiple of $1.5$ and $S_1 = 0.25$.}
\label{fig:minerva1p5_sprob}
\end{centering}
\end{figure}
\subsection{Maximum Risk as a Function of Round and Margin}
We also study the proportion of audits that stopped when the underlying election was a tie.
This proportion should approach a value less than the risk limit, $0.1$, as more audits are performed.

@@

Figures \ref{fig:minerva1_risk} and Figure~\ref{fig:minerva1p5_risk} show that fewer than $0.1$ of the audits stopped when the underlying election was a tie, for round multiples of $1.0$ and $1.5$ respectively, as would be expected for an RLA with risk limit $0.1$. 
Unlike EOR \BRAVO, the experimental risks here are much closer to the risk limit,
showing that \Minerva stops on average with a less conservative risk; \Minerva is sharper.

\begin{figure}
\begin{centering}
\includegraphics[width=0.6\textwidth]{minerva_multiround_1x_10^4/total_risk.png}
\caption{This plot shows, for each state margin,
the fraction of \Minerva audits with a round size multiple of $1.0$ that stopped in any of the $5$ rounds when the underlying election was a tie.}
\label{fig:minerva1_risk}
\end{centering}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.8\textwidth]{minerva25percthen1p5_sprob.png}
\caption{This plot shows, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$, round size multiple of $1.5$ and $S_1 = 0.25$.}
\label{fig:minerva_25}
\end{centering}
\end{figure}
\subsection{Maximum Risk as a Function of Round and Margin}
We also study the proportion of audits that stopped when the underlying election was a tie.
This proportion should approach a value less than the risk limit, $0.1$, as more audits are performed.

@@

Figure~\ref{fig:minerva1p5_risk} show that fewer than $0.1$ of the audits stopped when the underlying election was a tie, for round multiples $1.5$, as would be expected for an RLA with risk limit $0.1$. 
Unlike EOR \BRAVO, the experimental risks here are much closer to the risk limit,
showing that \Minerva stops on average with a less conservative risk; \Minerva is sharper. The plot for round multiple $1.0$ is very similar.

%\begin{figure}
%\begin{centering}
%\includegraphics[width=0.6\textwidth]{minerva_multiround_1x_10^4/total_risk.png}
%\caption{This plot shows, for each state margin,
%the fraction of \Minerva audits with a round size multiple of $1.0$ that stopped in any of the $5$ rounds when the underlying election was a tie.}
%\label{fig:minerva1_risk}
%\end{centering}
%\end{figure}
